---
title: "Mathematical Models"
format:
  revealjs:
    width: 1200
    scrollable: true
    theme: [default, styles.scss]
    navigation-mode: vertical
    controls-layout: bottom-right
    controls-tutorial: true
    incremental: false 
    chalkboard:
      src: notes/chalkboard_1a.json
      storage: chalkboard_pres
      theme: whiteboard
      chalk-width: 4
knitr:
  opts_chunk: 
    echo: true
    eval: true
    message: false
    code-fold: true
    warnings: false
    comment: "#>" 
    
revealjs-plugins:
  - pointer
  - verticator
  
filters: 
  - reveal-header
  - code-fullscreen
  - reveal-auto-agenda
editor: source
---

```{r}
#| include: false
library(MASS)
library(tidyverse)
library(csucistats)
library(waffle)
library(patchwork)

theme_set(theme_bw() + 
            theme(
              axis.text.x = element_text(size = 24),
              axis.title = element_text(size = 30),
              plot.title = element_text(size = 48),
              strip.text = element_text(size = 20),
              legend.title = element_blank(),
              legend.text = element_text(size = 24)))

```



# Motivation

## Motivation

The `bacteria` data set contians information on whether bacteria (`y`: y or n) is present after utilizing treatments (`ap`: **a**ctive or **p**lacebo).

::: fragment
We are interesting in determine the proportion of having bacteria present is different for those taking an "active" or "placebo".
:::

## Comparing Proportions

We are interesting in determining if different groups see different proportions of a binary outcome.

We compute the proportions of observing the binary outcome in Group 1 and Group 2 and see if they are fundamentally different from each other.

## 2 by 2 Cross Tabulations

|         |           |           |
|---------|-----------|-----------|
| Groups  | Outcome 1 | Outcome 2 |
| Group 1 | $p_{11}$  | $p_{21}$  |
| Group 2 | $p_{12}$  | $p_{22}$  |


::: fragment
We want to compare $p_{11}$ and $p_{12}$, to determine if the probability of outcome 1 are the same for both groups.

:::

## Test Statistic

We can use both $p_{11}$ and $p_{12}$ to determine if there is a fundamental difference.

::: fragment
However, it will be more beneficial to utilize one statistic to contruct the sampling distribution.
:::

::: fragment
$$
T =  \hat p_{11} - \hat p_{12}
$$
:::

## Obtain Proportions in R

```{r}
#| echo: true
#| eval: false
#| code-fold: show

props_df(DATA, GROUP, DATAOUTCOME, VAL)
```

## Obtain Difference in R

```{r}
#| echo: true
#| eval: false
#| code-fold: show


props_df(DATA, GROUP, OUTCOME, VAL, diff = TRUE)
```

## Bacteria Example

```{r}
#| code-fold: show


props_df(bacteria, ap, y, "y")
```

## Bacteria Example

```{r}
#| code-fold: show


props_df(bacteria, ap, y, "y", TRUE)
```


# Central Limit Theorem

# Normal Distribution

# Variability of $\bar X$
